\input{main.tex}

\title{Cryptography Principles and Applications}

\begin{document}
\maketitle
\begin{frame}\frametitle{Purposes}
\begin{itemize}
\item Learn what the rigorous information security is.
\item Learn how to secure information rigorously.
\item Learn how mathematics interplays with engineering.
\item \emph{Learn some English at least.}
\end{itemize}
\end{frame}
\begin{frame}\frametitle{Things to remember}
Cryptography is:
\begin{itemize}
\item A tremendous tool
\item The basis for many security mechanisms
\end{itemize}
Cryptography is \textbf{NOT}:
\begin{itemize}
\item The solution to all security problems
\item Reliable unless implemented and used properly
\item Something you should try to invent yourself	
\end{itemize}
\end{frame}
\begin{frame}\frametitle{Outline}
\begin{itemize}
\item Classic cryptography, Perfect Secrets
\item Private Key Encryption, MAC, Block Cipher, OWF
\item Number Theory, Factoring and Discrete Log
\item Key Management, Public Key, Digital Signature
\item Random Oracle Model, Cryptographic Protocols
\end{itemize}	
\end{frame}
\begin{frame}\frametitle{Textbooks \& Slides}
\begin{itemize}
\item \textbf{Introduction to Modern Cryptography}, \emph{Jonathan Katz and Yehuda Lindell}, Chapman \& Hall/CRC.
\item \textbf{Applied Cryptography: Protocols, Algorithms, and Source Code in C}, \emph{Bruce Schneier}, John Wiley \& Sons. (Chinese)
\item Dan Boneh's Cryptography @Stanford's Coursera.
\item Slides: https://github.com/YuZhang/crypto2014
\end{itemize}
\end{frame}
\begin{frame}\frametitle{Grades}
\begin{itemize}
\item Composition:
\begin{itemize}
\item Homework (30\%)
\item Final Exam (70\%)
\end{itemize}
\item How to score high:
\begin{itemize}
\item Read as much as you can.
\item Be skeptical about what you learn.
\item \alert{No Plagiarism!}
\end{itemize}
\end{itemize}
\end{frame}
\begin{frame}\frametitle{Contact}
\begin{description} 
\item[Office:] 710 Zong-He-Lou.
\item[Email:] yuni.zhang@gmail.com 
\end{description}
\end{frame}

\end{document}